Stats

### 2022-08-10 stats/analysis.Rmd
delete ext vali section

mAgeHedge <- brm(clickDistInBalloons ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataAgeHedge,
                    family = lognormal(),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 4)

@@

mAgeBox <- brm(correctBox ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataAgeBox,
                    family = bernoulli(link = "logit"),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 4)

@@

```{r splithalfr_hedge_kids_permutated}
# permutated splitting (random sampling without replacement)
splitscores_hedge_permutated_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  ncores = 7, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_hedge_kids_permutated_stratified}
# permutated splitting stratified by target position
splitscores_hedge_permutatedStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  ncores = 7, # setting ncores equally to something less than detectCores()
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_hedge_kids_montecarlo}
# monte carlo (sampling with replacement)
splitscores_hedge_montecarlo_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_hedge_kids_montecarlo_stratified}
# monte carlo stratified by target position
splitscores_hedge_montecarloStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_hedge_adults_permutated}
# permutated splitting (random sampling without replacement)
splitscores_hedge_permutated_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  ncores = 7, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_hedge_adults_permutated_stratified}
# permutated splitting stratified by target position
splitscores_hedge_permutatedStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  ncores = 7, # setting ncores equally to something less than detectCores()
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_hedge_adults_montecarlo}
# monte carlo (sampling with replacement)
splitscores_hedge_montecarlo_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_hedge_adults_montecarlo_stratified}
# monte carlo stratified by target position
splitscores_hedge_montecarloStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_box_kids_permutated}
# permutated splitting (random sampling without replacement)
splitscores_box_permutated_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  ncores = 7, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_box_kids_permutated_stratified}
# permutated splitting stratified by target position
splitscores_box_permutatedStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  ncores = 7, # setting ncores equally to something less than detectCores()
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_box_kids_montecarlo}
# monte carlo (sampling with replacement)
splitscores_box_montecarlo_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_box_kids_montecarlo_stratified}
# monte carlo stratified by target position
splitscores_box_montecarloStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_box_adults_permutated}
# permutated splitting (random sampling without replacement)
splitscores_box_permutated_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  ncores = 7, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_box_adults_permutated_stratified}
# permutated splitting stratified by target position
splitscores_box_permutatedStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  ncores = 7, # setting ncores equally to something less than detectCores()
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_box_adults_montecarlo}
# monte carlo (sampling with replacement)
splitscores_box_montecarlo_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_box_adults_montecarlo_stratified}
# monte carlo stratified by target position
splitscores_box_montecarloStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

@@

```{r save_splithalf_data}
write.csv(splithalf_data, "../saves/gafo-splithalf.csv", quote = F, row.names = F)
saveRDS(splithalf_data, file = "../saves/gafo-splithalf-table.rds")
```

## Test-retest reliability

@@

# run model
mRetestHedge <- brm(clickDistInBalloons ~ age + (0 + reliday | subjID), 
                              data   = mDataRetestHedge, 
                              family = lognormal(), 
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 4)

@@

ggsave("../figures/gafo_hedge_retest_kids.png", width = 6, height = 4)
```

@@

ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
```

```{r retest_box_data}
# take data of first reli day for internal consistency
box_retest <- reli %>% 
  filter(studyversion == "box") %>% 
  group_by(subjID, reliday, sample, ageInYears) %>% 
  tidyboot_mean(column = correctBox, na.rm = TRUE)

@@

# check how many there are
box_retest %>% 
  group_by(sample) %>%
  filter(mean_reliday1 >= mean(mean_reliday1, na.rm = T) + 3*sd(mean_reliday1, na.rm = T) | 
         mean_reliday1 <= mean(mean_reliday1, na.rm = T) - 3*sd(mean_reliday1, na.rm = T) |
         mean_reliday2 >= mean(mean_reliday2, na.rm = T) + 3*sd(mean_reliday2, na.rm = T) |
         mean_reliday2 <= mean(mean_reliday2, na.rm = T) - 3*sd(mean_reliday2, na.rm = T))
```

@@

# run model
mRetestBox <- brm(correctBox ~ age + (0 + reliday | subjID), 
                              data   = mDataRetestBox, 
                              family = bernoulli(link = "logit"),
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 4)

@@

ggsave("../figures/gafo_box_retest_kids.png", width = 6, height = 4)
```

@@

ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
```

@@

```{r arrange_plots}
ggarrange(

@@

ggsave("../figures/gafo_results_GLMM.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
```

```{r}
ggarrange(hedge_variation_plot,
          NULL,
          ggarrange(
              hedge_intCon_kids, 
              hedge_retest_kids, 
              nrow = 1, 
              ncol = 2, 
              labels = c("B", "C")
            ), 
          nrow = 3, heights = c(0.625, 0.05, 0.325), labels = c("A", "", "")
)

ggsave("/Users/julia_prein/Downloads/gafo_poster.png", width = 6.5, height = 6, scale = 1.1, bg = "white")
```

# EXTERNAL VALIDITY

```{r extvali_prepareData}
mDataExtvali <- testtrials %>% 
  filter(ageInYears < 6) %>% 
  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, symmetricPosition) %>% 
  group_by(subjID) %>% 
  # so that all models run with same nr of subjects
  drop_na() %>% 
  ungroup() %>% 
  mutate(
    # centered around minimum
    hhSibs = siblingsNr, 
    sibsChildAged = siblingsChildAged,

    # centered around mean
    trial = scale(trialNr, center = TRUE, scale = FALSE)[,1],
    ccAge = scale(childcareAge, center = TRUE, scale = FALSE)[,1],
    ccHours = scale(childcareHours, center = TRUE, scale = FALSE)[,1],
    hhTotal = scale(householdTotal, center = TRUE, scale = FALSE)[,1],

    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
    peerExposure = scale(childcareHours, center = TRUE, scale = TRUE) + scale(siblingsNr, center = TRUE, scale = TRUE)[,1],
    pe = scale(peerExposure, center = TRUE, scale = TRUE)[,1], 
  ) %>% 
  select(datacollection, studyversion, subjID, trial, age, targetPosition, symmetricPosition, correctBox, ccAge, ccHours, hhTotal, hhSibs, sibsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, pe) %>% 
  mutate_if(is.character, as.factor)

n_distinct(mDataExtvali$subjID)
```

```{r extvali_nullmodel}
mExtvalinull <- brm(correctBox ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataExtvali,
                    family = bernoulli(link = "logit"),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 4)
```

```{r extvali_fullmodels}
mExtvaliccAge <- update(mExtvalinull,
                      newdata = mDataExtvali,
                      formula = correctBox ~ ccAge + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
                      family = bernoulli(link = "logit"),
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mExtvaliccHours <- update(mExtvalinull,
                      newdata = mDataExtvali,
                      formula = correctBox ~ ccHours + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
                      family = bernoulli(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mExtvalihhTotal <- update(mExtvalinull,
                      newdata = mDataExtvali,
                      formula = correctBox ~ hhTotal + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
                      family = bernoulli(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mExtvalihhSibs <- update(mExtvalinull,
                      newdata = mDataExtvali,
                      formula = correctBox ~ hhSibs + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
                      family = bernoulli(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mExtvalisibsChildAged <- update(mExtvalinull,
                      newdata = mDataExtvali,
                      formula = correctBox ~ sibsChildAged + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
                      family = bernoulli(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mExtvalisiblingsVarietyScoreP <- update(mExtvalinull,
                      newdata = mDataExtvali,
                      formula = correctBox ~ siblingsVarietyScoreP + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
                      family = bernoulli(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mExtvalisiblingsVarietyScoreW <- update(mExtvalinull,
                      newdata = mDataExtvali,
                      formula = correctBox ~ siblingsVarietyScoreW + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
                      family = bernoulli(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mExtvaliPE <- update(mExtvalinull,
                      newdata = mDataExtvali,
                      formula = correctBox ~ pe + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
                      family = bernoulli(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)
```

```{r extvali_modelcomparisons}
mExtvalinull <- add_criterion(mExtvalinull, "waic")
mExtvaliccAge <- add_criterion(mExtvaliccAge, "waic")
mExtvaliccHours <- add_criterion(mExtvaliccHours, "waic")
mExtvalihhTotal <- add_criterion(mExtvalihhTotal, "waic")
mExtvalihhSibs <- add_criterion(mExtvalihhSibs, "waic")
mExtvalisibsChildAged <- add_criterion(mExtvalisibsChildAged, "waic")
mExtvalisiblingsVarietyScoreP <- add_criterion(mExtvalisiblingsVarietyScoreP, "waic")
mExtvalisiblingsVarietyScoreW <- add_criterion(mExtvalisiblingsVarietyScoreW, "waic")
mExtvaliPE <- add_criterion(mExtvaliPE, "waic")

mExtvaliComparison <- as_tibble(loo_compare(mExtvalinull, mExtvaliccAge, mExtvaliccHours, mExtvalihhTotal, mExtvalihhSibs, mExtvalisibsChildAged, mExtvalisiblingsVarietyScoreP, mExtvalisiblingsVarietyScoreW, mExtvaliPE, criterion = "waic"), rownames = "model")

mExtvaliComparison

mExtvaliComparisonWeights <- as_tibble(model_weights(mExtvalinull, mExtvaliccAge, mExtvaliccHours, mExtvalihhTotal, mExtvalihhSibs, mExtvalisibsChildAged, mExtvalisiblingsVarietyScoreP, mExtvalisiblingsVarietyScoreW, mExtvaliPE, criterion = "waic"), rownames = "model")

mExtvaliComparisonWeights %>% arrange(-value)

extvaliModelorder <- mExtvaliComparisonWeights %>% arrange(value) %>%  pull(model)
```

```{r extvali_savemodels}
write.csv(mExtvalinull, "../saves/extvali-mExtvalinull.csv", quote = F, row.names = F)
saveRDS(mExtvalinull, "../saves/extvali-mExtvalinull.rds")

write.csv(mExtvaliccAge, "../saves/extvali-mExtvaliccAge.csv", quote = F, row.names = F)
saveRDS(mExtvaliccAge, "../saves/extvali-mExtvaliccAge.rds")

write.csv(mExtvaliccHours, "../saves/extvali-mExtvaliccHours.csv", quote = F, row.names = F)
saveRDS(mExtvaliccHours, "../saves/extvali-mExtvaliccHours.rds")

write.csv(mExtvalihhTotal, "../saves/extvali-mExtvalihhTotal.csv", quote = F, row.names = F)
saveRDS(mExtvalihhTotal, "../saves/extvali-mExtvalihhTotal.rds")

write.csv(mExtvalihhSibs, "../saves/extvali-mExtvalihhSibs.csv", quote = F, row.names = F)
saveRDS(mExtvalihhSibs, "../saves/extvali-mExtvalihhSibs.rds")

write.csv(mExtvalisibsChildAged, "../saves/extvali-mExtvalisibsChildAged.csv", quote = F, row.names = F)
saveRDS(mExtvalisibsChildAged, "../saves/extvali-mExtvalisibsChildAged.rds")

write.csv(mExtvalisiblingsVarietyScoreP, "../saves/extvali-mExtvalisiblingsVarietyScoreP.csv", quote = F, row.names = F)
saveRDS(mExtvalisiblingsVarietyScoreP, "../saves/extvali-mExtvalisiblingsVarietyScoreP.rds")

write.csv(mExtvalisiblingsVarietyScoreW, "../saves/extvali-mExtvalisiblingsVarietyScoreW.csv", quote = F, row.names = F)
saveRDS(mExtvalisiblingsVarietyScoreW, "../saves/extvali-mExtvalisiblingsVarietyScoreW.rds")

write.csv(mExtvaliPE, "../saves/extvali-mExtvaliPE.csv", quote = F, row.names = F)
saveRDS(mExtvaliPE, "../saves/extvali-mExtvaliPE.rds")
```

```{r extvali_save}
extvali_results <- mExtvaliComparison %>%
  left_join(mExtvaliComparisonWeights) %>%
  select(model, waic, se_waic, value, elpd_diff, se_diff) %>%
  rename(
    Predictor = model, 
    WAIC = waic, 
    SE_WAIC = se_waic,
    Weight = value, 
    ELPD_DIFF = elpd_diff, 
    SE_ELPD_DIFF = se_diff,
  ) %>% 
  mutate(
    Predictor = recode(Predictor, 
                   "mExtvaliPE" = "Peer exposure index", 
                   "mExtvalisiblingsVarietyScoreW" = "Sibling variety score (Cassidy et al., 2005)", 
                   "mExtvalihhSibs" = "# Children in household aged 0-18", 
                   "mExtvaliccHours" = "Average hours spent in childcare per day",
                   "mExtvalinull" = "Null model", 
                   "mExtvalihhTotal" = "# Household members",
                   "mExtvaliccAge" = "Age of childcare entry", 
                   "mExtvalisiblingsVarietyScoreP" = "Sibling variety score (Peterson, 2000)", 
                   "mExtvalisibsChildAged" = "# Children in household aged 1-12",
                   )
  )

write.csv(extvali_results, "../saves/extvali-results.csv", quote = F, row.names = F)
saveRDS(extvali_results, "../saves/extvali-results.rds")
```

```{r extvali_posteriordraws}
extvali_draws <- bind_rows(
  mExtvaliccAge %>% gather_draws(b_ccAge),
  mExtvaliccHours %>% gather_draws(b_ccHours), 
  mExtvalihhTotal %>% gather_draws(b_hhTotal), 
  mExtvalihhSibs %>% gather_draws(b_hhSibs), 
  mExtvalisibsChildAged %>% gather_draws(b_sibsChildAged), 
  mExtvalisiblingsVarietyScoreP %>% gather_draws(b_siblingsVarietyScoreP), 
  mExtvalisiblingsVarietyScoreW %>% gather_draws(b_siblingsVarietyScoreW),
  mExtvaliPE %>% gather_draws(b_pe)
  ) %>% 
  mutate(
    Predictor = factor(.variable, 
                       levels = c("b_hhSibs", 
                                  "b_siblingsVarietyScoreP", 
                                  "b_sibsChildAged", 
                                  "b_hhTotal", 
                                  "b_ccHours", 
                                  "b_ccAge", 
                                  "b_siblingsVarietyScoreW", 
                                  "b_pe"), 
                       labels = c("# Children in household aged 0-18", 
                                  "Sibling variety score (Peterson, 2000)", 
                                  "# Children in household aged 1-12", 
                                  "# Household members", 
                                  "Average hours spent in childcare per day", 
                                  "Age of childcare entry", 
                                  "Sibling variety score (Cassidy et al., 2005)", 
                                  "Peer exposure index")
                       )  
  )

write.csv(extvali_draws, "../saves/extvali-draws.csv", quote = F, row.names = F)
saveRDS(extvali_draws, "../saves/extvali-draws.rds")
```

```{r extvali_plot}
ggplot(extvali_draws, aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 3) +
    labs(x = "Posterior estimate", y = "")+
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("grey","#85AD00")) +
  xlim(-0.2, 0.6) +
  theme_minimal()

ggsave("../figures/extvali_results_all.png", width = 10, height = 6, scale = 0.7, bg = "white")

>>>>

mAgeHedge <- brm(clickDistInBalloons ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataAgeHedge,
                    family = lognormal(),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 100)

@@

mAgeBox <- brm(correctBox ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataAgeBox,
                    family = bernoulli(link = "logit"),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 100)

@@

```{r splithalfr_hedge_kids_permutated}
# permutated splitting (random sampling without replacement)
splitscores_hedge_permutated_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  ncores = 100, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_hedge_kids_permutated_stratified}
# permutated splitting stratified by target position
splitscores_hedge_permutatedStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  ncores = 100, # setting ncores equally to something less than detectCores()
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_hedge_kids_montecarlo}
# monte carlo (sampling with replacement)
splitscores_hedge_montecarlo_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 100, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_hedge_kids_montecarlo_stratified}
# monte carlo stratified by target position
splitscores_hedge_montecarloStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 100, # setting ncores equally to something less than detectCores()
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_hedge_adults_permutated}
# permutated splitting (random sampling without replacement)
splitscores_hedge_permutated_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  ncores = 100, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_hedge_adults_permutated_stratified}
# permutated splitting stratified by target position
splitscores_hedge_permutatedStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  ncores = 100, # setting ncores equally to something less than detectCores()
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_hedge_adults_montecarlo}
# monte carlo (sampling with replacement)
splitscores_hedge_montecarlo_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 100, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_hedge_adults_montecarlo_stratified}
# monte carlo stratified by target position
splitscores_hedge_montecarloStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 100, # setting ncores equally to something less than detectCores()
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_box_kids_permutated}
# permutated splitting (random sampling without replacement)
splitscores_box_permutated_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  ncores = 100, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_box_kids_permutated_stratified}
# permutated splitting stratified by target position
splitscores_box_permutatedStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  ncores = 100, # setting ncores equally to something less than detectCores()
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_box_kids_montecarlo}
# monte carlo (sampling with replacement)
splitscores_box_montecarlo_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 100, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_box_kids_montecarlo_stratified}
# monte carlo stratified by target position
splitscores_box_montecarloStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 100, # setting ncores equally to something less than detectCores()
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_box_adults_permutated}
# permutated splitting (random sampling without replacement)
splitscores_box_permutated_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  ncores = 100, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_box_adults_permutated_stratified}
# permutated splitting stratified by target position
splitscores_box_permutatedStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  ncores = 100, # setting ncores equally to something less than detectCores()
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

@@

```{r splithalfr_box_adults_montecarlo}
# monte carlo (sampling with replacement)
splitscores_box_montecarlo_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 100, # setting ncores equally to something less than detectCores()
)

@@

```{r splithalfr_box_adults_montecarlo_stratified}
# monte carlo stratified by target position
splitscores_box_montecarloStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 100, # setting ncores equally to something less than detectCores()
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

@@

```{r save_splithalf_data}
write.csv(splithalf_data, "../saves/gafo-splithalf.csv", quote = F, row.names = F)
saveRDS(splithalf_data, file = "../saves/gafo-splithalf-table.rds")

# clean up
rm(list = ls(pattern = "^splitscores"))
```

## Test-retest Reliability - Hedge

@@

# run model
mRetestHedge <- brm(clickDistInBalloons ~ age + (0 + reliday | subjID), 
                              data   = mDataRetestHedge, 
                              family = lognormal(), 
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 100)

@@

saveRDS(hedge_retest_kids, file = "../saves/gafo-hedge-retest-kids.rds")
# ggsave("../figures/gafo_hedge_retest_kids.png", width = 6, height = 4)
```

@@

saveRDS(hedge_retest_adults, file = "../saves/gafo-hedge-retest-adults.rds")
# ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
```

## Test-retest Reliability - Box

```{r retest_box_data}
box_retest <- reli %>% 
  filter(studyversion == "box") %>% 
  group_by(subjID, reliday, sample, ageInYears) %>% 
  tidyboot_mean(column = correctBox, na.rm = TRUE)

@@

# check how many there are => there are none!
box_retest %>% 
  group_by(sample) %>%
  filter(mean_reliday1 >= mean(mean_reliday1, na.rm = T) + 3*sd(mean_reliday1, na.rm = T) | 
         mean_reliday1 <= mean(mean_reliday1, na.rm = T) - 3*sd(mean_reliday1, na.rm = T) |
         mean_reliday2 >= mean(mean_reliday2, na.rm = T) + 3*sd(mean_reliday2, na.rm = T) |
         mean_reliday2 <= mean(mean_reliday2, na.rm = T) - 3*sd(mean_reliday2, na.rm = T))
```

@@

# run model
mRetestBox <- brm(correctBox ~ age + (0 + reliday | subjID), 
                              data   = mDataRetestBox, 
                              family = bernoulli(link = "logit"),
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 100)

@@

saveRDS(box_retest_kids, file = "../saves/gafo-box-retest-kids.rds")
# ggsave("../figures/gafo_box_retest_kids.png", width = 6, height = 4)
```

@@

saveRDS(box_retest_adults, file = "../saves/gafo-box-retest-adults.rds")
# ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
```

@@

```{r arrange_plots}
gafo_arrangedplot <- ggarrange(

@@

gafo_arrangedplot
saveRDS(gafo_arrangedplot, file = "../saves/gafo-arrangedplot.rds")
# ggsave("../figures/gafo_arrangedplot.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
```
